\textbf{Discrete Bulk Reconstruction Problem} \\ \large Compiled Research

### 2025-03-12 paper.tex
added

\begin{figure}[htbp]  % 'h' places the figure "here" (can be adjusted)
    \centering
    \includegraphics[width=\textwidth]{vertex_subregions.jpeg}  % Adjust width as needed
    \caption{This illustration shows cuts for single subregions of a system. This does not address the challenges of DBRP about finding a set of edge weights such that ALL possible min-cuts match ALL given boundary entropies simultaneously. Therefore, in order to show min-cuts and edge weights for S(ABC), S(ADB), etc. We will have to implement properties in order to make sure our solution for each subregion is accurate.}  % Caption text
    \label{fig:single subregion min-cut}  % Label for referencing
\end{figure}
\newpage 
\section{Required Properties}
To ensure a solution exists we \textbf{need} the following properties:

>>>>

\begin{figure}[htbp]  % 'h' places the figure "here" (can be adjusted)
    \centering
    \includegraphics[width=\textwidth]{vertex_subregions.jpeg}  % Adjust width as needed
    \caption{This illustration shows the process of DBRP and demonstrates a simple min-cut for a single subregion (D). The key challenge of the DBRP is finding a set of edge weights such that ALL possible min-cuts match ALL given boundary entropies simultaneously. For more complex combinations like S(ABC), S(ABD), etc., additional entropy constraints must be implemented to ensure the solution accurately represents the entanglement structure of the boundary theory.}  % Caption text
    \label{fig:single subregion min-cut}  % Label for referencing
\end{figure}
\newpage 
\section{Required Properties}
To ensure a solution exists we \textbf{need} the following properties:
